Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-16 thirdPaper/draft/typeConeAssociahedra.tex
minor change

\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
\begin{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{thm:allPolytopalRealizationsNKC}

>>>>

\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
\begin{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{@{}l@{}} \b{z} \ge 0, \quad \b{z}_\omega = 0 \text{ for any straight or self-kissing walk } \omega, \\ \text{and } \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{thm:allPolytopalRealizationsNKC}
